Recent Advances in Networking

### 2013-07-26 Compiled/chapter4/sections/Collaboration-Use-Cases.tex
Fix compilation of chapter4 with new pdf files for figures

\begin{figure}[tbp]
   \begin{subfigure}[]{0.4\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures/snapshot_nond.eps}}
   \caption{Unbiased Gnutella}%
   \end{subfigure}
\hfill
   \begin{subfigure}[]{0.45\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures/snapshot_nd.eps}}
   \caption{Gnutella with Oracle}%
   \end{subfigure}   \caption{Visualization of Gnutella overlay topology}
   \label{fig:oracle:gnutella_topology}
\end{figure}

@@

\begin{figure}[tbp]
	\begin{subfigure}[]{0.32\linewidth}
     {\includegraphics[width=1\textwidth]{figures/asdist.eps}}
    \caption{Mean AS distance in Underlay\label{fig:oracle:gnutella_metric:2a}}
    \end{subfigure}
 \hfill
    \begin{subfigure}[]{0.32\linewidth}
    {\includegraphics[width=1\textwidth]{figures/intraAS-leaf.eps}}
    \caption{Intra-AS peerings (\%) for Leaf nodes\label{fig:oracle:gnutella_metric:2b}}
    \end{subfigure}
 \hfill
    \begin{subfigure}[]{0.32\linewidth}
    {\includegraphics[width=1\textwidth]{figures/intraAS-up.eps}}
    \caption{Intra-AS peerings (\%) for Ultrapeers\label{fig:oracle:gnutella_metric:2c}}
    \end{subfigure}
    \caption{Metrics for Gnutella simulations}
   \label{fig:oracle:gnutella_metric}
\end{figure}

@@

\begin{figure}[tbp]
  \center\includegraphics[width=0.8\linewidth]{figures/trafficShift-concept.eps}
  \caption{By choosing a CDI server for a client with the help of CaTE, traffic
  engineering goals and accurate end-user server assignment become possible.}
  \label{fig:flowSelection}
  \vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
    \center \includegraphics[width=3.2in]{figures/CaTE_Schematic.eps}
  \vspace{-0.1in}
    \caption{CaTE System architecture and flow of messages.}
    \label{fig:CaTE-architecture}
    \vspace{-0.2in}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=0.90\linewidth]{figures/trafficShift-illustration.eps}
\caption{Content-aware Traffic Engineering Process}
\label{fig:Content-aware-illustration2}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures/providersVsVolume.eps}
\caption{CDF of traffic volume of CDIs in ISP1.}
\label{fig:CDF-Traffic-CPs}
\vspace{-1.5em}
\end{figure}

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures/Volume_timeseries.eps}
\caption{Normalized traffic for top CDIs by volume in ISP1.}
\label{fig:CPs-Total-Traffic}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures/subnetVsVolumeBucket.eps}
\caption{Subnet diversity from which content is available.}
\label{fig:VolumeChoices}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center
\includegraphics[width=1\linewidth]{figures/SubnetChoice_r-2.eps}
\caption{Evolution over time of number of subnets for selected CDIs in the top 10 CDIs.}
\label{fig:TemporalEffect}
\vspace{-1.5em}
\end{figure}

>>>>

\begin{figure}[tbp]
   \begin{subfigure}[]{0.4\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures-pdf/snapshot_nond}}
   \caption{Unbiased Gnutella}%
   \end{subfigure}
\hfill
   \begin{subfigure}[]{0.45\linewidth}
     {\includegraphics[angle=-90,width=1\linewidth]{figures-pdf/snapshot_nd}}
   \caption{Gnutella with Oracle}%
   \end{subfigure}   \caption{Visualization of Gnutella overlay topology}
   \label{fig:oracle:gnutella_topology}
\end{figure}

@@

\begin{figure}[tbp]
	\begin{subfigure}[]{0.32\linewidth}
     {\includegraphics[width=1\textwidth]{figures-pdf/asdist}}
    \caption{Mean AS distance in Underlay\label{fig:oracle:gnutella_metric:2a}}
    \end{subfigure}
 \hfill
    \begin{subfigure}[]{0.32\linewidth}
    {\includegraphics[width=1\textwidth]{figures-pdf/intraAS-leaf}}
    \caption{Intra-AS peerings (\%) for Leaf nodes\label{fig:oracle:gnutella_metric:2b}}
    \end{subfigure}
 \hfill
    \begin{subfigure}[]{0.32\linewidth}
    {\includegraphics[width=1\textwidth]{figures-pdf/intraAS-up}}
    \caption{Intra-AS peerings (\%) for Ultrapeers\label{fig:oracle:gnutella_metric:2c}}
    \end{subfigure}
    \caption{Metrics for Gnutella simulations}
   \label{fig:oracle:gnutella_metric}
\end{figure}

@@

\begin{figure}[tbp]
  \center\includegraphics[width=0.8\linewidth]{figures-pdf/trafficShift-concept}
  \caption{By choosing a CDI server for a client with the help of CaTE, traffic
  engineering goals and accurate end-user server assignment become possible.}
  \label{fig:flowSelection}
  \vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
    \center \includegraphics[width=3.2in]{figures-pdf/CaTE_Schematic}
  \vspace{-0.1in}
    \caption{CaTE System architecture and flow of messages.}
    \label{fig:CaTE-architecture}
    \vspace{-0.2in}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=0.90\linewidth]{figures-pdf/trafficShift-illustration}
\caption{Content-aware Traffic Engineering Process}
\label{fig:Content-aware-illustration2}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures-pdf/providersVsVolume}
\caption{CDF of traffic volume of CDIs in ISP1.}
\label{fig:CDF-Traffic-CPs}
\vspace{-1.5em}
\end{figure}

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures-pdf/Volume_timeseries}
\caption{Normalized traffic for top CDIs by volume in ISP1.}
\label{fig:CPs-Total-Traffic}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center\includegraphics[width=1\linewidth]{figures-pdf/subnetVsVolumeBucket}
\caption{Subnet diversity from which content is available.}
\label{fig:VolumeChoices}
\vspace{-1.5em}
\end{figure}

@@

\begin{figure}[tbp]
\center
\includegraphics[width=1\linewidth]{figures-pdf/SubnetChoice_r-2}
\caption{Evolution over time of number of subnets for selected CDIs in the top 10 CDIs.}
\label{fig:TemporalEffect}
\vspace{-1.5em}
\end{figure}

### 2013-07-26 Compiled/chapter4/sections/Traffic-Trends-Server-Diversity.tex
Fix compilation of chapter4 with new pdf files for figures

\begin{figure}[tbp]
  \centering
  \includegraphics[height=0.7\linewidth]{figures/dns-diversity.eps}
  \caption{DNS replies for two different sites hosted on a CDI, in two-hour bins}%
  \label{fig:dns_diversity}
\end{figure}

@@

\begin{figure}[tbp]
   \center
   \includegraphics[height=0.7\linewidth,angle=-90]{figures/avgResponseSize.ps}\\
   \includegraphics[height=0.7\linewidth,angle=-90]{figures/avgResponseSubnetSize.ps}

@@

\begin{figure}[tbp]
  \center
   \includegraphics[height=0.7\linewidth,angle=-90]{figures/14day-returnedIPCDF-bytes.ps}
   \includegraphics[height=0.7\linewidth,angle=-90]{figures/14day-returnedIPCDF-hits.ps}
  \caption{CDF of \# of IPs for the ISP DNS resolver normalized by traffic
    volume  (top) and requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.)}
  \label{fig:CDF-IPPAF-IPs}
\end{figure}

\begin{figure}[tbp]
  \center
   \includegraphics[height=0.7\linewidth,angle=-90]{figures/SubnetsByBytes.ps}
   \includegraphics[height=0.7\linewidth,angle=-90]{figures/SubnetsByHits.ps}
  \caption{CDF of \# of subnets for ISP DNS resolver normalized by traffic
    volume  (top) and by requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.)}
  \label{fig:CDF-IPPAF-Subnets}
\end{figure}

@@

We find that more than $50$\perc of the volume or requests can be served by
more than one IP address. Similarly, there is choice between at least two
subnets over $40$\perc of the time across both metrics, see Figure~\ref
{fig:CDF-IPPAF-Subnets}. This indicates that there is significant potential for
the ISP to bias the location preference of the CDI.

\begin{figure}[tbp]
  \center\includegraphics[height=0.7\linewidth,angle=-90]{figures/maxTTLCDF.ps}
  \caption{CDF of DNS TTL value by traffic volume and by number of requests.}
  \label{fig:CDF-IPPAF-TTL}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[height=0.7\linewidth]{figures-pdf/dns-diversity}
  \caption{DNS replies for two different sites hosted on a CDI, in two-hour bins}%
  \label{fig:dns_diversity}
\end{figure}

@@

\begin{figure}[htbp]
   \center
   \includegraphics[height=0.7\linewidth]{figures-pdf/avgResponseSize}\\
   \includegraphics[height=0.7\linewidth]{figures-pdf/avgResponseSubnetSize}

@@

\begin{figure}[htbp]
  \center
   \includegraphics[height=0.7\linewidth]{figures-pdf/14day-returnedIPCDF-bytes}
   \includegraphics[height=0.7\linewidth]{figures-pdf/14day-returnedIPCDF-hits}
  \caption{CDF of \# of IPs for the ISP DNS resolver normalized by traffic
    volume  (top) and requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.)}
  \label{fig:CDF-IPPAF-IPs}
\end{figure}

\begin{figure}[htbp]
  \center
   \includegraphics[height=0.7\linewidth]{figures-pdf/SubnetsByBytes}
   \includegraphics[height=0.7\linewidth]{figures-pdf/SubnetsByHits}
  \caption{CDF of \# of subnets for ISP DNS resolver normalized by traffic
    volume  (top) and by requests (bottom) including aggregation on
    domain levels. (Logarithmic x-axis.)}
  \label{fig:CDF-IPPAF-Subnets}
\end{figure}

@@

We find that more than $50$\perc of the volume or requests can be served by
more than one IP address. Similarly, there is choice between at least two
subnets over $40$\perc of the time across both metrics, see Figure~\ref
{fig:CDF-IPPAF-Subnets}. This indicates that there is significant potential for
the ISP to bias the location preference of the CDI.
\clearpage
\begin{figure}[htbp]
  \center\includegraphics[height=0.7\linewidth]{figures-pdf/maxTTLCDF}
  \caption{CDF of DNS TTL value by traffic volume and by number of requests.}
  \label{fig:CDF-IPPAF-TTL}
\end{figure}
